---
title: "CCES Specific PassivePacker Folder Manipulation Script"
author: "Kourtney Burger"
date: "2023-10-05"
output: html_document
---

# GENERAL PLAN

0.  Manipulate data folder structure using DataFolderManipulation.Rmd to prepare data paths for passive packer
1.  Download Deployment Details spreadsheet and save to folder within project
2.  Manipulate Deployment Details spreadsheet to align with passive packer fields
3.  Add additional passive packer fields
4.  Connect to passive packer database and append it

# Required Packages

```{r}
library(here)
library(DBI)
library(RSQLite)
library(tidyverse)
library(rjson)
library(dplyr)
library(stringr)
```

# Set Working Directory

```{r}
DepDir <- here('ADRIFT-Deployment-PassivePacker')
```

# Taiki's helper function for dates

Helper function to create all the "2020-01-01T00:00:00" formatted date strings that JSON will want. *Note that this requires that you convert all your dates in the deploy details data that you read in earlier (or anywhere else you might read dates from) to POSIXct format.*

```{r}
posixToText <- function(x) {
    format(x, '%Y-%m-%dT%H:%M:%S')
}

posixToText(as.POSIXct("2018-11-22 08:28:24", tz='UTC'))
```

# Import and Prep Data

```{r}
# Import Deployment Details
deployDetails <- read.csv("DeploymentDetailsFiles/CCES_DeploymentDetails.csv")

# Change soundtrap names
deployDetails[deployDetails == 'ST640'] <- 'SoundTrap 640'
deployDetails[deployDetails == "ST4300HF"] <- "SoundTrap 4300 High Frequency"
deployDetails[deployDetails == "ST300"] <- "SoundTrap 300"
deployDetails[deployDetails == "ST4300"] <- "SoundTrap 4300 Standard"
deployDetails[deployDetails == "ST500HF"] <- "SoundTrap 500 High Frequency"
deployDetails[deployDetails == "ST300HF"] <- "SoundTrap 300 High Frequency"

# Change Site Names
deployDetails[deployDetails == "WAS"] <- "Washington"
deployDetails[deployDetails == "COL"] <- "Columbia River"
deployDetails[deployDetails == "ORE"] <- "Oregon"
deployDetails[deployDetails == "HUM"] <- "Humboldt"
deployDetails[deployDetails == "MND"] <- "Mendocino"
deployDetails[deployDetails == "PTA"] <- "Point Arena"
deployDetails[deployDetails == "SFB"] <- "San Francisco Bay"
deployDetails[deployDetails == "HMB"] <- "Half Moon Bay"
deployDetails[deployDetails == "MBY"] <- "Monterey Bay"
deployDetails[deployDetails == "MOB"] <- "Morro Bay"
deployDetails[deployDetails == "CHI"] <- "Channel Islands"
deployDetails[deployDetails == "LAB"] <- "Los Angeles Basin"
deployDetails[deployDetails == "SND"] <- "San Diego"
deployDetails[deployDetails == "BCN"] <- "Baja California Norte"
deployDetails[deployDetails == "BCS"] <- "Baja California Sur"

# ADDITIONAL DATA CLEANING
deployDetails$Data_Start <- as.POSIXct(deployDetails$Data_Start, format = "%m/%d/%Y %H:%M:%S", tz = 'UTC')
deployDetails$Data_End <- as.POSIXct(deployDetails$Data_End, format = "%m/%d/%Y %H:%M:%S", tz = 'UTC')

deployDetails$Deployment_Date <- as.POSIXct(deployDetails$Deployment_Date, format = "%m/%d/%Y %H:%M", tz = 'UTC')
deployDetails$Recovery_Date <- as.POSIXct(deployDetails$Recovery_Date, format = "%m/%d/%Y %H:%M", tz = 'UTC')

deployDetails$Quality_Category <- str_to_title(deployDetails$Quality_Category)

# convert numeric data to characters
deployDetails <- deployDetails %>%
        mutate(across(where(is.numeric), as.character))
```

```{r}
# Import Passive Packer data table 
db <- dbConnect(SQLite(), "PassivePacker_v.4.0.3-win64/database/packageData.sqlite")
ppdt <- dbReadTable(db, "DEPLOYMENT_DATA")
dbDisconnect(db)
```

```{r}
## Prepare data to append to Passive Packer table

### Subset data
dd <- subset(deployDetails, select = c('Project', 'DeploymentID', 'Cruise'))

### Add required columns
dd <- dd %>%
  add_column(ID = NA, SITE_CRUISE = NA, PACKAGE_ID = NA, SOURCE_PATH = NA,
             DESTINATION_PATH = NA, METADATA_AUTHOR = 'Kourtney Burger', 
             META_AUTHOR_UUID = NA, PUBLICATION_DATE = NA, PLATFORM = NA, 
             INSTRUMENT_TYPE = NA, INSTRUMENT_ID = NA, DEPLOYMENT_ALIAS = NA,
             SITE_ALIAS = NA, DEPLOY_TIME = NA, AUDIO_START_TIME = NA,
             RECOVER_TIME =NA, AUDIO_END_TIME = NA, TITLE = "California Current Ecosystems Survey - Passive Acoustics Survey", 
             PURPOSE = "From Report", ABSTRACT = "From Report", DATA_COMMENT = NA, 
             TEMP_PATH = NA, BIO_PATH = NA, OTHER_PATH = NA, DOCS_PATH = "Y:/1651_CCES_2018/Report", 
             CALIBRATION_PATH = NA, CREATION_TIME = NA, UPDATE_TIME = NA, 
             USE = 'Y', SAMPLING_DETAILS = NA, QUALITY_DETAILS = NA, 
             SCIENTISTS = NA, SPONSERS = NA, FUNDERS = NA, SENSORS = NA, 
             DEPLOYMENT_DETAILS = NA, CALIBRATION_INFO = NA, DATASET_INFO = NA, 
             ANCILLARY_INFO = NA)

### Reorder and rename columns
dd <- dd[, c(4,1,2,5,3,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,
             26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42)]

colnames(dd) <- c('ID','PROJECT','DEPLOYMENT_ID','SITE_CRUISE','SITE_OR_CRUISE',
                  'PACKAGE_ID','SOURCE_PATH','DESTINATION_PATH','METADATA_AUTHOR',
                  'META_AUTHOR_UUID','PUBLICATION_DATE','PLATFORM',
                  'INSTRUMENT_TYPE', 'INSTRUMENT_ID','DEPLOYMENT_ALIAS',
                  'SITE_ALIAS','DEPLOY_TIME', 'AUDIO_START_TIME','RECOVER_TIME',
                  'AUDIO_END_TIME','TITLE','PURPOSE','ABSTRACT','DATA_COMMENT',
                  'TEMP_PATH','BIO_PATH','OTHER_PATH','DOCS_PATH',
                  'CALIBRATION_PATH','CREATION_TIME','UPDATE_TIME','USE',
                  'SAMPLING_DETAILS','QUALITY_DETAILS','SCIENTISTS','SPONSORS',
                  'FUNDERS','SENSORS','DEPLOYMENT_DETAILS','CALIBRATION_INFO',
                  'DATASET_INFO','ANCILLARY_INFO') 

### Add ID Number (Primary Key) 
# If no existing data, maxID is 0
oldMax <- ifelse(nrow(ppdt) == 0, 0, max(ppdt$ID))
dd$ID <- (1:nrow(dd)) + oldMax

### Fix project and package_id fields
#(combine columns and remove spaces)
dd$PROJECT <- paste('SWFSC-',dd$PROJECT)
dd$PACKAGE_ID <- paste(dd$PROJECT,'_',dd$DEPLOYMENT_ID)
dd$PROJECT <- paste('["',dd$PROJECT,'"]')
dd$PROJECT <- gsub(" ","",dd$PROJECT)
dd$PACKAGE_ID <- gsub(" ","",dd$PACKAGE_ID)

# Add site alias
for (i in 1:nrow(deployDetails)) {
  dd$SITE_ALIAS[i] <- deployDetails$Site[i]
}

### Dataset Description
dd$PURPOSE <- 'The 2018 California Current Ecosystem Survey (CCES) was a multidisciplinary survey of the marine ecosystem from southern British Columbia, Canada to northern Baja California, Mexico. This survey was a collaboration between the Southwest Fisheries Science Center’s (SWFSC) Fishery Resource Division (FRD) and Marine Mammal and Turtle Division (MMTD). The survey included oceanographic measurements, use of multi-frequency echosounders, surface trawls, vertically and obliquely integrating net tows, continuous underway fish egg sampling, visual line-transect surveys for marine mammals, photographic capture-recapture studies of marine mammals, strip transect surveys for seabirds, and passive acoustic surveys of marine mammals using Drifting Acoustic Spar Buoy Recorders (DASBRs). The recordings collected in this project have been analyzed to detect echolocation signals from beaked whales, sperm whales, and dwarf and pygmy sperm whales.'
dd$ABSTRACT <- 'The data from this deployment was collected using Drifting Acoustic Spar Buoy Recorders (DASBRs). DASBRs are free floating instruments with two hydrophones, in a vertical array, and a digital recorder. CCES 2018 was the second survey conducted under the Pacific Marine Assessment Program for Protected Species (PacMAPPS), supported by the National Oceanographic and Atmospheric Administration (NOAA), the US Navy, and the Bureau of Ocean Energy Management (BOEM). This study conducts annual cetacean and ecosystem surveys throughout the North Pacific and generates data products used by all three agencies to meet regulatory requirements pertaining to protected species.' 

### Set package destination (change once hard drive is ready)  
dd$DESTINATION_PATH <- 'F:/Packaged Drifts'
```

# JSON Strings

## Sampling Details Column

```{r}
for(i in 1:nrow(dd)) {
#  for(i in 2) {
  newSdList <- list(
    '1' = list(
        'channel_start' = posixToText(deployDetails$Data_Start[i]),
        'channel_end' = posixToText(deployDetails$Data_End[i]),
        'sensor' = deployDetails$ChannelNumber_1[i],
        'sampling details' = list(
            list(
                'type' = 'duty_cycle_widget',
                'value_1' = deployDetails$RecordingDuration_m[i],
                'value_2' = deployDetails$RecordingInterval_m[i],
                'checked' = FALSE,
                'start' = posixToText(deployDetails$Data_Start[i]),
                'end' = posixToText(deployDetails$Data_End[i])
            ),
            list(
                'type' = 'sample_rate_widget',
                'value_1' = deployDetails$SampleRate_kHz[i],
                'value_2' = '16',
                'checked' = FALSE,
                'start' = posixToText(deployDetails$Data_Start[i]),
                'end' = posixToText(deployDetails$Data_End[i])
            )
        )
    ),
    '2' = list(
        'channel_start' = posixToText(deployDetails$Data_Start[i]),
        'channel_end' = posixToText(deployDetails$Data_End[i]),
        'sensor' = deployDetails$ChannelNumber_2[i],
        'sampling details' = list(
            list(
                'type' = 'duty_cycle_widget',
                'value_1' = deployDetails$RecordingDuration_m[i],
                'value_2' = deployDetails$RecordingInterval_m[i],
                'checked' = FALSE,
                'start' = posixToText(deployDetails$Data_Start[i]),
                'end' = posixToText(deployDetails$Data_End[i])
            ),
            list(
                'type' = 'sample_rate_widget',
                'value_1' = deployDetails$SampleRate_kHz[i],
                'value_2' = '16',
                'checked' = FALSE,
                'start' = posixToText(deployDetails$Data_Start[i]),
                'end' = posixToText(deployDetails$Data_End[i])
            )
        )
    )
)
  dd$SAMPLING_DETAILS[i] <- toJSON(newSdList)
}


# Comment once working
# Copy text from database
# sdText <- '{"1": {"channel_start": "2018-07-30T00:00:00", "channel_end": "2018-10-12T23:59:59", "sensor": "1", "sampling details": [{"type": "duty_cycle_widget", "value_1": "2", "value_2": "4", "checked": false, "start": "2018-07-30T00:00:00", "end": "2018-08-18T23:58:00"}, {"type": "duty_cycle_widget", "value_1": "2", "value_2": "20", "checked": false, "start": "2018-08-19T00:18:00", "end": "2018-10-12T23:59:59"}, {"type": "sample_rate_widget", "value_1": "256", "value_2": "16", "checked": false, "start": "2018-07-30T00:00:00", "end": "2018-10-12T23:59:59"}]}, "2": {"channel_start": "2018-07-30T00:00:00", "channel_end": "2018-10-12T23:59:59", "sensor": "2", "sampling details": [{"type": "duty_cycle_widget", "value_1": "2", "value_2": "4", "checked": false, "start": "2018-07-30T00:00:00", "end": "2018-08-18T23:58:00"}, {"type": "duty_cycle_widget", "value_1": "2", "value_2": "20", "checked": false, "start": "2018-08-19T00:18:00", "end": "2018-10-12T23:59:59"}, {"type": "sample_rate_widget", "value_1": "256", "value_2": "16", "checked": false, "start": "2018-07-30T00:00:00", "end": "2018-10-12T23:59:59"}]}}'
# sdList <- fromJSON(sdText)
# cat(toJSON(newSdList))
# cat(toJSON(sdList))
# #view(newSdList)
# #View(sdList)
# identical(newSdList,sdList)
```

## Quality Details Column

```{r}
for(i in 1:nrow(dd)) {
#  for(i in 1) {
    newQdList <- list(
      'analyst' = 'Cory Hom-Weaver',
      'analyst_uuid' = '',
      'quality_details' = list(
        list(
          'quality' = 'Good',
          'low_freq' = deployDetails$Quality_LowFreq[i],
          'high_freq' = deployDetails$Quality_HighFreq[i],
          'start' = posixToText(deployDetails$Data_Start[i]),
          'end' = posixToText(deployDetails$Data_End[i]),
          'comments' = paste('Refer to ', deployDetails$Data_ID[i], '_500Hz_LF_Noise_Log.xls' , ' for detailed noise logs.', sep = ""),
          'channels' = list(
            1)
        )
      ),
      'method' = '',
      'objectives' = '',
      'abstract' = ''
    )

# save newQdList to r list
dd$QUALITY_DETAILS[i] <- toJSON(newQdList)
}

# Comment once working
# Copy example text from database
# qdText <- '{"analyst": "Cory Hom-Weaver", "analyst_uuid": "", "quality_details": [{"quality": "Good", "low_freq": "0", "high_freq": "256000", "start": "2018-07-30T00:00:00", "end": "2018-10-12T23:59:59", "comments": "Refer to CCES_004_500Hz_LF_Noise_Log.xls for detailed noise logs.", "channels": [1]}], "method": "", "objectives": "", "abstract": ""}'
# qdList <- fromJSON(qdText)
# cat(toJSON(newQdList))
# cat(toJSON(qdList))
# #view(newQdList)
# #View(qdList)
# identical(newQdList,qdList)
```

## Scientists Column

```{r}
# This will be the same for each drift within a project
# PASCAL - Shannon Rankin
# CCES - Shannon Rankin and Anne Simonis
# ADRIFT - Shannon Rankin & Chief sci from deployment details

for (i in 1:nrow(dd)) {
#  for (i in 1) {

  newSciList <- list(
    list(
      'name' = 'Anne Simonis',
      'uuid' = '3e9e1d2e-0fed-45d0-bc21-c388d4ea933a'
    ),
    list(
      'name' = 'Shannon Rankin',
      'uuid' = 'c6a8953f-616b-4de1-99ce-3dd70e631dd5'
    )
  )

  dd$SCIENTISTS[i] <- toJSON(newSciList)
}


# Comment once working
# Copy text from database
# sciText <- '[{"name": "Anne Simonis", "uuid": "3e9e1d2e-0fed-45d0-bc21-c388d4ea933a"}, {"name": "Shannon Rankin", "uuid": "c6a8953f-616b-4de1-99ce-3dd70e631dd5"}]'
# sciList <- fromJSON(sciText)
# cat(toJSON(newSciList))
# cat(toJSON(sciList))
# #view(newSciList)
# #View(sciList)
# identical(newSciList,sciList)
```

## Sponsers Column

```{r}
# This will always be NOAA SWFSC

for (i in 1:nrow(dd)) {
#  for (i in 1) {

   newSponList <- list(
    list(
      'name' = 'NOAA SWFSC',
      'uuid' = '918a8687-8b33-4f70-b550-79a5273866fa'
    )
  )

  dd$SPONSORS[i] <- toJSON(newSponList)
}

# Comment once working
# Copy text from database
# sponText <- '[{"name": "NOAA SWFSC", "uuid": "918a8687-8b33-4f70-b550-79a5273866fa"}]'
# sponList <- fromJSON(sponText)
# cat(toJSON(newSponList))
# cat(toJSON(sponList))
# #view(newSponList)
# #View(sponList)
# identical(newSponList,sponList)
```

## Funders Column

```{r}
# This will always be NOAA SWFSC

for (i in 1:nrow(dd)) {
#  for (i in 1) {

  newFunList <- list(
    list(
      'name' = 'NOAA SWFSC',
      'uuid' = '918a8687-8b33-4f70-b550-79a5273866fa'
    ),
    list(
      'name' = 'BOEM',
      'uuid' = 'fee4d17a-a7dd-4f13-ade5-817b4f1fc86d'
    ),
    list(
      'name' = 'US Navy Pacific Fleet Environmental Readiness Division',
      'uuid' = 'd246d0dc-b74b-4dc3-8d27-bdbb28b3e009'
    )
  )

  dd$FUNDERS[i] <- toJSON(newFunList)
}

# Comment once working
# Copy text from database
# funText <- '[{"name": "NOAA SWFSC", "uuid": "918a8687-8b33-4f70-b550-79a5273866fa"}, {"name": "BOEM", "uuid": "fee4d17a-a7dd-4f13-ade5-817b4f1fc86d"}, {"name": "US Navy Pacific Fleet Environmental Readiness Division", "uuid": "d246d0dc-b74b-4dc3-8d27-bdbb28b3e009"}]'
# funList <- fromJSON(funText)
# cat(toJSON(newFunList))
# cat(toJSON(funList))
# #view(newFunList)
# #View(funList)
# identical(newFunList,funList)
```

## Sensors Column

```{r}
# A lot of this data has to come from the calibration sheet
# For CCES, all calibration info is in 'CCES2018_CalibrationInfo.csv'
# For PASCAL, make spreadsheet from report
# For ADRIFT, use inventory spreadsheets

# read in data from calibration info spreadsheet
calInfo <- read.csv("Calibration Files/CCES2018_CalibrationInfo.csv")

for(i in 1:nrow(dd)) {
#  for (i in 1) {
  newSenList <- list(
    '0' = list(
      'type' = 'Audio Sensor',
      'number' = '1',
      'id' = as.character(calInfo$SerialNumber_1[i]),
      'name' = calInfo$HydrophoneType_1[i],
      'pos_x' = '',
      'pos_y' = '',
      'pos_z' = '-100',
      'value_1' = as.character(calInfo$SerialNumber_1[i]),
      'value_2' = '',
      'description' = ''
    ),
    '1' = list(
      'type' = 'Audio Sensor',
      'number' = '2',
      'id' = as.character(calInfo$SerialNumber_2[i]),
      'name' = calInfo$HydrophoneType_2[i],
      'pos_x' = '',
      'pos_y' = '',
      'pos_z' = '-105',
      'value_1' = as.character(calInfo$SerialNumber_2[i]),
      'value_2' = '',
      'description' = ''
    ),
    '2' = list(
      'type' = 'Depth Sensor',
      'number' = '3',
      'id' = deployDetails$Depth_Sensor[i],
      'name' = deployDetails$DepthSensorType[i],
      'pos_x' = '',
      'pos_y' = '',
      'pos_z' = '-100',
      'value_1' = '',
      'value_2' = '',
      'description' = ''
    ),
    '3' = list(
      'type' = 'Other Sensor',
      'number' = '4',
      'id' = deployDetails$GPS_ID[i],
      'name' = deployDetails$GPS_Tracker[i],
      'pos_x' = '',
      'pos_y' = '',
      'pos_z' = '+1',
      'value_1' = 'GPS',
      'value_2' = '',
      'description' = '2 SPOT sattelite GPS sensors'
    )
  )

dd$SENSORS[i] <- toJSON(newSenList)
}


# Comment once working
# Copy text from database
# senText <- '{"0": {"type": "Audio Sensor", "number": "1", "id": "856073", "name": "HTI-92-WB", "pos_x": "", "pos_y": "", "pos_z": "-100", "value_1": "856073", "value_2": "", "description": ""}, "1": {"type": "Audio Sensor", "number": "2", "id": "856040", "name": "HTI-96-min", "pos_x": "", "pos_y": "", "pos_z": "-105", "value_1": "856040", "value_2": "", "description": ""}, "2": {"type": "Depth Sensor", "number": "3", "id": "OT-6", "name": "NA", "pos_x": "", "pos_y": "", "pos_z": "-100", "value_1": "", "value_2": "", "description": ""}, "3": {"type": "Other Sensor", "number": "4", "id": "E/K", "name": "SPOT", "pos_x": "", "pos_y": "", "pos_z": "+1", "value_1": "GPS", "value_2": "", "description": "2 SPOT sattelite GPS sensors"}}'
# senList <- fromJSON(senText)
# cat(toJSON(newSenList))
# cat(toJSON(senList))
# #view(newSenList)
# #View(senList)
# identical(newSenList,senList)
```

## Deployment Details Column

```{r}
for(i in 1:nrow(dd)) {
#  for (i in 1) {
    newDdList <- list(
      'DEPLOY_TYPE' = 'Mobile Marine',
      'SEA_AREA' = 'North Pacific Ocean',
      'DEPLOY_SHIP' = deployDetails$Deploy_Vessel[i],
      'FILES' = paste('F:/CCES_RawData/manipulated/gps/',deployDetails$Data_ID[i],'/',deployDetails$Data_ID[i],'_GPS.csv',',','F:/CCES_RawData/manipulated/gps/',deployDetails$Data_ID[i],'/',deployDetails$Data_ID[i],'_DeploymentDepth.csv',sep = ""),
      'POSITION_DETAILS' = 'Satellite gps'
    )
    
dd$DEPLOYMENT_DETAILS[i] <- toJSON(newDdList)
}

# Comment once working
# Copy text from database 
# ddText <- '{"DEPLOY_TYPE": "Mobile Marine", "SEA_AREA": "North Pacific Ocean", "DEPLOY_SHIP": "R/V Ruben Lasker", "FILES": "F:/CCES_RawData/manipulated/gps/CCES_004/CCES_004_GPS.csv", "POSITION_DETAILS": "Satellite gps"}'
# ddList <- fromJSON(ddText)
# cat(toJSON(newDdList))
# cat(toJSON(ddList))
# #view(newDdList)
# #View(ddList) 
# identical(newDdList,ddList)
```

## Calibration info column

```{r}
for(i in 1:nrow(dd)) {
#  for (i in 1) {
    
    newCalList <- list(
    'CAL_STATE' = 'Factory Calibrated',
    'CAL_DOCS_PATH' = 'F:/CCES_RawData/calInfo', 
    'SENSITIVITY' = '',
    'FREQUENCY' = '',
    'GAIN' = '',
    'COMMENT' = 'This dataset is composed of multichannel recorders with different types of hydrophones, each with its own unique sensitivity and frequency range. For the detailed calibration information refer to the CCES2018_CalibrationInfo.csv spreadsheet.'
    )
dd$CALIBRATION_INFO[i] <- toJSON(newCalList)
}

# comment once working
# Copy text from database 
# calText <- '{"CAL_STATE": "Factory Calibrated", "CAL_DOCS_PATH": "F:/CCES_RawData/calInfo", "SENSITIVITY": "", "FREQUENCY": "", "GAIN": "", "COMMENT": "This dataset is composed of multichannel recorders with different types of hydrophones, each with its own unique sensitivity and frequency range. For the detailed calibration information refer to the CCES2018_CalibrationInfo.csv spreadsheet."}'
# calList <- fromJSON(calText)
# cat(toJSON(newCalList))
# cat(toJSON(calList))
# #view(newCalList)
# #View(calList) 
# identical(newCalList,calList)
```

## Dataset info column

```{r}
for(i in 1:nrow(dd)) {
#  for (i in 1) {
  newDiList <- list(
    'TYPE' = 'Raw',
    'SUB_TYPE' = 'Audio',
    'PLATFORM' = 'Drifter',
    'INSTRUMENT_TYPE' = deployDetails$Type[i],
    'INSTRUMENT_ID' = deployDetails$Instrument_ID[i],
    'DEPLOYMENT_TIME' = posixToText(deployDetails$Deployment_Date[i]),
    'RECOVERY_TIME' = posixToText(deployDetails$Recovery_Date[i]),
    'AUDIO_START' = posixToText(deployDetails$Data_Start[i]),
    'AUDIO_END' = posixToText(deployDetails$Data_End[i]),
    'SOURCE_PATH' =  paste('F:/CCES_RawData/manipulated/audio/',deployDetails$Data_ID[i], sep = ""), 
    'DATA_COMMENT' = deployDetails$Notes[i]
  )
dd$DATASET_INFO[i] <- toJSON(newDiList)
}

# comment once working
# Copy text from database 
# diText <- '{"TYPE": "Raw", "SUB_TYPE": "Audio", "PLATFORM": "Drifter", "INSTRUMENT_TYPE": "SM3M", "INSTRUMENT_ID": "SM3M_3", "DEPLOYMENT_TIME": "2018-07-25T03:30:00", "RECOVERY_TIME": "2018-10-13T00:36:00", "AUDIO_START": "2018-07-30T00:00:00", "AUDIO_END": "2018-10-12T23:59:59", "SOURCE_PATH": "F:/CCES_RawData/manipulated/audio/CCES_004", "DATA_COMMENT": "Duty cycle 2/4 for 20 days then 2/20, Instrument noise at ~60kHz and 100kHz throughout drift"}'
# diList <- fromJSON(diText)
# cat(toJSON(newDiList))
# cat(toJSON(diList))
# #view(newDiList)
# #View(diList) #comment once running full loop
# identical(newDiList,diList)
```

## Ancillary Info Column

```{r}
for(i in 1:nrow(dd)) {
#  for (i in 1) {

    newAncilList <- list(
    'BIO_PATH' = "",
    'OTHER_PATH' = paste('F:/CCES_RawData/manipulated/metadata/', deployDetails$Data_ID[i], sep = ""),
    'TEMP_PATH' = paste('F:/CCES_RawData/manipulated/temp/', deployDetails$Data_ID[i], sep = "")
  )

dd$ANCILLARY_INFO[i] <- toJSON(newAncilList)
}

# comment once working
# ancilText <- '{"BIO_PATH":"","OTHER_PATH":"F:/CCES_RawData/manipulated/metadata/CCES_004","TEMP_PATH":"F:/CCES_RawData/manipulated/temp/CCES_004"}'
# ancilList <- fromJSON(ancilText)
# cat(toJSON(newAncilList))
# cat(toJSON(ancilList))
# #view(newAncilList)
# #View(ancilList) #comment once running full loop
# identical(newAncilList,ancilList)
```

# Append to passive packer table

```{r}
con <- dbConnect(SQLite(), "PassivePacker_v.4.0.3-win64/database/packageData.sqlite")
dbAppendTable(con, 'DEPLOYMENT_DATA', dd)
dbDisconnect(con)
```